The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications

### 2016-10-06 paper.tex
updated doc
updated title and affiliation

\title{Linear Optics Interferometry}

@@

\author{Peter P. Rohde}
\email[]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\affiliation{Centre for Quantum Computation and Intelligent Systems (QCIS), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

@@

\section{Mathematical Background}

@@

\section{Optical Encoding of Quantum Information}

\subsection{Single-Photons}

@@

\subsubsection{Dual-Rail}

\subsubsection{Time-Bins}

\subsection{Continuous-Variables}

\subsubsection{Coherent States}

\subsubsection{Squeezed States}

\section{Efficient Circuit Decompositions of Linear Optics Networks}

@@

\section{Experimental Implementation}

\subsection{State Preparation}

\subsubsection{Single-Photons}

\subsubsection{Bell Pairs}

\subsubsection{Coherent States}

\subsubsection{Squeezed States}

\subsection{Linear Optics Networks}

\subsubsection{Bulk Optics}

@@

\subsubsection{Time-Bins}

@@

\section{Applications for Linear Optics Interferometry}

\subsection{Linear Optics Quantum Computation}

\subsection{Boson-Sampling}

\subsection{Quantum Metrology}

@@

\subsection{Encrypted Quantum Computation}

\section{State of the Art}

>>>>

\title{The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications}

@@

\author{Peter P. Rohde}
\email[]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\affiliation{Centre for Quantum Software \& Information (CQSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

@@

\section{Mathematical background}

@@

\section{Optical encoding of quantum information}

\subsection{Single-photons}

@@

\subsubsection{Dual-rail}

\subsubsection{Time-bins}

\subsection{Continuous-variables}

\subsubsection{Coherent states}

\subsubsection{Squeezed states}

\section{Efficient circuit decompositions of linear optics networks}

@@

\section{Experimental implementation}

\subsection{State preparation}

\subsubsection{Single-photons}

\subsubsection{Bell pairs}

\subsubsection{Coherent states}

\subsubsection{Squeezed states}

\subsection{Linear optics networks}

\subsubsection{Bulk-optics}

@@

\subsubsection{Time-bins}

@@

\section{Applications for linear optics interferometry}

\subsection{Linear optics quantum computation}

\subsection{Boson-sampling}

\subsection{Quantum metrology}

@@

\subsection{Encrypted quantum computation}

\section{State of the art}
